### 2021-11-26 input/proposal.tex
text after proof to motivate fs plus

\begin{lemma}[\label{def:detection}$\textup{FB}^+ \wedge \textup{FS}
  \implies$ \underline{D}etector existence (D)]
  Assuming $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on
  $\pi_{xz}$ of $\alpha_x$ with $\alpha_x = \min D_z$, if $x$
  broadcasts a staleness notification $\delta_x$, either $z$
  eventually delivers it, or a \process $y$ in such a chain of
  delivery $\pi_{xz}'$ eventually detects its blocking.
  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
\end{lemma}

@@

To reach dynamic consistent partitioning, the detecting \process must
broadcast a message notifying the \emph{possible} staleness of its
last delivered and forwarded message to its \emph{downstream}
\processes. Indeed, Figure~\ref{fig:undoproblem} shows that from
detector's perspective, the chain of events is identical, yet it must
react to the worst case scenario where $\delta_a$ existed and was
blocked. \TODO{More about figure.} \TODO{Challenging?}

>>>>

\begin{lemma}[\label{lem:detector}$\textup{FB}^+ \wedge \textup{FS}
  \implies$ \underline{D}etector existence (D)]
  Assuming $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on
  $\pi_{xz}$ of $\alpha_x$ with $\alpha_x = \min D_z$, if $x$
  broadcasts a staleness notification $\delta_x$, either $z$
  eventually delivers it, or a \process $y$ in such a chain of
  delivery $\pi_{xz}'$ eventually detects its blocking.
  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
\end{lemma}

@@

Proof of Lemma~\ref{lem:detector} shows that there exists false
positive in the blocking detection: $\delta_x$ may not exist but $y'$
still receives $\alpha_s$ after the delivery of $\delta_s$ from the
path it delivered $\alpha_x$. Figure~\ref{fig:undoproblem} highlights
this behavior. In Figure~\ref{fig:undoproblemB}, $a$ does not delete
its partition. In Figure~\ref{fig:undoproblemD} and because of \NAMEB,
$c$ received the same series of messages as in
Figure~\ref{fig:problemD}. Yet, $c$ must assume the existence of
$\delta_a$ and act accordingly by forcing the staleness of its best
delivered message and disseminate this information to its neighbors.
To avoid flooding the system with false positive staleness
notifications, we propose to reduce the scope of staleness
notifications by including only downstream \processes. In
Figure~\ref{fig:undoproblemD}, false positives would not affect $a$
and $b$.
